

\chapter{Hardware for IoT Projects}\label{hardware-for-iot-projects}

\FILENAME\

When teaching programming you may find yourself in a situation that
things can be done on your computer, but you may not want to install
programs that help you to learn programming on your computer. However,
we have a solution (or several) for you. We will have some fun with
hardware for IoT that at the same time can be used to teach you some
very elementary skills in programming. However, if you would rather use
your computer you certainly can do this too.

We see the following arguments for using IoT hardware:

\begin{itemize}

\item
  You will have fun with inexpensive hardware
\item
  You will get hands on experience with IOT devices
\item
  You will learn how to program in python
\item
  You can keep your current computer unchanged
\item
  You will get experience with two platforms esp8266 and Raspberry PI 3
\item
  You can customise your choices by conducting some fun projects.
\item
  You have the opportunity to find alternative hardware choices such as
  the WiPy or the ESP32. You may find cheaper or better alternatives if
  you buy kits when they are available. And learn in getting an overview
  about such devices and kits.
\end{itemize}

\emph{Note:} Ordering from overseas suppliers may take significant time,
so make sure to plan ahead. Prices given here are done to provide an
estimate, they may vary.

\section{Raspberry Pi 3}\label{raspberry-pi-3}

The raspberry PI 3 is a very good development platform. With its base
price of \$35 it is quite a bargain. You will need some additional
components to make sure you can use it. Please be reminded to never
connect or power the raspberry with your computers USB port. It draws
some significant amperage and we do not want you to destroy your
computer. We recommend that you buy a certified power adapter. The price
is so cheap that you could even create your own mini cluster as a
project. We do not recommend any older versions of Raspberry as they are
less powerful and do not contain built-in Bluetooth or WiFi.

\emph{Configuration:}

\begin{itemize}

\item
  \$37.50
  \href{https://www.amazon.com/Raspberry-Model-A1-2GHz-64-bit-quad-core/dp/B01CD5VC92/ref=sr_1_1?s=pc\&ie=UTF8\&qid=1499251061\&sr=1-1\&keywords=raspberry+pi+3}{Pi
  3}
\item
  \$7.69
  \href{https://www.amazon.com/Eleduino-Raspberry-Model-Acrylic-Enclosure/dp/B01CQRROLW/ref=sr_1_7?s=electronics\&ie=UTF8\&qid=1499251106\&sr=1-7\&keywords=raspberry+pi+3+case}{Case}
\item
  \$7.99
  \href{https://www.amazon.com/Enokay-Supply-Raspberry-Charger-Adapter/dp/B01MZX466R/ref=sr_1_3?ie=UTF8\&qid=1498443576\&sr=8-3\&keywords=raspberry+pi+power+adapter+micro+usb+switch}{Power
  Adapter} This is an aftermarket poweradapter. Lots uof us use this
  one.
\item
  \$6.99
  \href{https://www.amazon.com/AmazonBasics-High-Speed-HDMI-Cable-Standard/dp/B014I8SSD0/ref=sr_1_3?ie=UTF8\&qid=1499253502\&sr=8-3\&keywords=hdmi+cable}{HDMI
  cable}
\item
  Monitor/TV with hdmi
\item
  SD Card, 8GB minimum, 32GB maximum
\end{itemize}

\emph{Advantages:}

\begin{itemize}

\item
  Full Linux like OS based on debian
\item
  Good environment for learning Linux and Python
\item
  Reasonable interfaces to IoT sensors
\item
  excellent camera support
\item
  excellent choice of expansion packages including Grove Sensors that
  make it easy to attach sensors and actuators. An example package is
  the
  \href{https://www.amazon.com/GrovePi-Starter-Kit-Dexter-Industries/dp/B00TXTZ5SQ/ref=pd_lpo_vtph_147_bs_tr_img_1?_encoding=UTF8\&psc=1\&refRID=45QX6XSNZAG1NT8NES79}{Grove
  Starter Kit} for about \$90
\end{itemize}

\emph{Disadvantages:}

\begin{itemize}

\item
  We tried the Windows IoT package and were not impressed by it. This is
  not an issue of the Raspberry, but the Windows IoT platform
\end{itemize}

\section{ESP8266 Robot Car Kit}\label{esp8266-robot-car-kit}

The ESP8266 has many variants. Some of which are difficult to interface
with. However, this does not apply for the ESP8266 NodeMCU. This board
is originally flashed with \emph{Lua}, however it can easily be
reflashed with MicroPython. In addition it is often offered as part of a
platform to develop a robot car. There are arguably better kits
available, but the price of \$24 for the entire kit is hard to beat.
Unfortunately the version of python, as well as the limited memory make
the esp8266 not a full fledged platform for python programming and you
will quickly see its limitations. Interfacing with it, however, as an
IoT device will gain you a lot of insights.

\emph{Configuration:}

\begin{itemize}

\item
  \$14.99
  \href{https://www.amazon.com/KOOKYE-ESP8266-NodeMcu-ESP-12E-Expansion/dp/B01C6MR62E/ref=sr_1_1?ie=UTF8\&qid=1499251895\&sr=8-1\&keywords=esp8266+robot+car}{esp8266
  \& shield} or
  \href{https://www.amazon.com/Makerfocus-ESP8266-ESP-12E-Development-Expansion/dp/B01MU4XQUN/ref=sr_1_2?ie=UTF8\&qid=1499252002\&sr=8-2\&keywords=esp8266+motor+shield}{esp8266
  \& shield}
\item
  \$12.59
  \href{https://www.amazon.com/Emgreat-Chassis-Encoder-wheels-Battery/dp/B00GLO5SMY/ref=pd_rhf_se_s_cp_10?_encoding=UTF8\&pd_rd_i=B00GLO5SMY\&pd_rd_r=77XYGK6BE54FGDTGQ0AC\&pd_rd_w=FNQFl\&pd_rd_wg=wKMdb\&psc=1\&refRID=77XYGK6BE54FGDTGQ0AC}{Chasis}
\item
  4 * AA Rechargable Batteries \& charger
\end{itemize}

Optionally you may want to get additional sensors such as wheel Encoders

\begin{itemize}

\item
  \href{https://www.amazon.com/Wheel-Encoder-Kit-Robot-Car/dp/B00NPWGEIM/ref=sr_1_4?s=toys-and-games\&ie=UTF8\&qid=1499254488\&sr=1-4\&keywords=speed+sensor+robot+car+wheel}{Wheel
  Encoder}
\end{itemize}

\emph{Advantages:}

\begin{itemize}
\item
  Very low price for what it can do
\item
  We have OSX software available that makes it easy to setup (Other
  tutorials for other platforms are available on the internet, you can
  contribute by creating documentation we distribute in class for
  points)
\item
\item
\end{itemize}

\section{Sensor Kit}\label{sensor-kit}

It is fun to attach sensors to your IoT board. There are many kits
ab{]}vailable and we encourage you to do comparisions. One such kit is

\begin{itemize}

\item
  \$29.99
  \href{https://www.amazon.com/Elegoo-Upgraded-Modules-Tutorial-Arduino/dp/B01MG49ZQ5/ref=sr_1_7?s=electronics\&ie=UTF8\&qid=1499251441\&sr=1-7\&keywords=elegoo}{Elegoo
  37 Sensors}
\end{itemize}

However it does not include a breadboard like other kits. Hence we
recommend that you get a breadboard as it makes experimenting easier.

\begin{itemize}

\item
  \$5.68
  \href{https://www.amazon.com/Elegoo-Premium-Female-tie-points-breadboard/dp/B06XB8TZVC/ref=sr_1_23?s=electronics\&ie=UTF8\&qid=1499251600\&sr=1-23\&keywords=elegoo}{small
  bread board and wires}
\end{itemize}

\section{Fish Kit}\label{fish-kit}

\begin{itemize}

\item
  \$29.99
  \href{https://www.amazon.com/Swimmer-Inflatable-Flying-Replacement-Balloon/dp/B00658LN3E/ref=pd_bxgy_21_img_2?_encoding=UTF8\&pd_rd_i=B00658LN3E\&pd_rd_r=F71N2YCYE6Z0BCCEPQJC\&pd_rd_w=AwYab\&pd_rd_wg=rHTnv\&psc=1\&refRID=F71N2YCYE6Z0BCCEPQJC}{shark}

  \begin{itemize}

  \item
    cheaper balloons leak
  \item
    before assembly and putting gas in, make sure components work.
  \item
    gas will last typically for one week
  \item
    \$39.99 gas can be purchased in party store
  \end{itemize}
\item
  2 g9 servo
\item
  soldering (for cable, so cheap one will do)
\item
  pins
\item
  esp
\item
  double sided scotch tape
\item
  hot glue gun
\item
  paper clips
\end{itemize}

\section{Alternative components}\label{alternative-components}

\subsection{Esp8266 Alternatives}\label{esp8266-alternatives}

Two models are good. Adafruit has some added features, but may need
soldering

\begin{itemize}

\item
  \$8.79
  \href{https://www.amazon.com/HiLetgo-Version-NodeMCU-Internet-Development/dp/B010O1G1ES/ref=sr_1_3?s=electronics\&ie=UTF8\&qid=1499251149\&sr=1-3\&keywords=esp8266}{NodeMCU}
\item
  \$16.95 \href{https://www.adafruit.com/product/2821}{Adafruit Feather}
\end{itemize}

\subsection{Car Parts Alternatives}\label{car-parts-alternatives}

\begin{itemize}

\item
  \$14.59
  \href{https://www.amazon.com/Ardokit-Chassis-Encoder-Battery-Arduino/dp/B00K5OWHXO/ref=sr_1_3?s=electronics\&ie=UTF8\&qid=1499251712\&sr=1-3\&keywords=robot+car}{Car
  Chasis}
\item
  \$22.88
  \href{https://www.amazon.com/VKmaker-Avoidance-tracking-Chassis-Ultrasonic/dp/B01CXVA6IO/ref=sr_1_6?s=electronics\&ie=UTF8\&qid=1499251770\&sr=1-6\&keywords=robot+car}{Car
  Chasis and Arduino}
\end{itemize}

\subsection{Simple sensors}\label{simple-sensors}

Simple sensors can be attached to the boards with cables (that you need
to purchase separately). Examples include

\begin{itemize}

\item
  \href{https://www.amazon.com/Elegoo-Sensor-Module-Arduino-MEGA/dp/B009OVGKTQ/ref=sr_1_5?s=electronics\&ie=UTF8\&qid=1500678010\&sr=1-5\&keywords=grove+sensor}{Elegoo
  37 sensor kit}
\item
  \href{https://www.amazon.com/Breadboard-Wires-Aoyoho-Multicolored-Jumper/dp/B01GK2Q4ZQ/ref=sr_1_1?s=electronics\&ie=UTF8\&qid=1500678142\&sr=1-1\&keywords=bread+board+cab\%3Be}{Breadboard
  Cable}
\end{itemize}

\subsection{Grove Sensors}\label{grove-sensors}

Grove sensors have ready-made cables that make them easy to attach to
the Raspberry PI. However, they are more expensive. You still need a
Raspberry PI. No soldering iron and no breadboards are required.

\begin{itemize}

\item
  \href{https://www.seeedstudio.com/Grove-Starter-Kit-for-Arduino-p-1855.html}{Grove
  Starter Set}
\item
  \href{https://www.seeedstudio.com/category/Grove-c-1003.html}{Seed
  Studio Grove Sensors}
\item
  \href{https://www.seeedstudio.com/Grove-Base-Shield-for-NodeMCU-p-2513.html}{Grove
  Shield for NodeMCU}
\item
  \href{http://www.switchdoc.com/2016/02/tutorial-intro-to-grove-connectors-for-arduinoraspberry-pi-projects/}{Grove
  Cable}
\end{itemize}

\section{Alternative Hardware and Sensors}

In this section we will list a number of alternative hardware products
that we are exploring. If you have used them, please help us improving
these sections.

\subsection{Small Footprint Battery Power}

The following board providesto the Raspberry Pi a lithium battery
power pack expansion board. It is powered by two 18650 Li-ion
batteries providing steady. A 4-LED indicator indicates the level of
charge. The board costs \$16.99.

\URL{https://www.sunfounder.com/plus-power-module.html}
